---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tibble)
```

# badata

<!-- badges: start -->
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/badata)](https://CRAN.R-project.org/package=badata) -->
[![DOI](https://zenodo.org/badge/584811775.svg)](https://zenodo.org/badge/latestdoi/584811775)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

**badata** is a data package that provides data from the German Federal Employment Agency (Bundesagentur für Arbeit -- BA) about unemployed persons, employees, and jobs in Germany from 2012 to 2021 by district (Kreis) and occupational group.

## Installation

You can install the development version of **badata** from [GitHub](https://github.com/RegioHub/badata) with:

``` r
# install.packages("devtools")
devtools::install_github("RegioHub/badata")
```

## Usage

**badata** provides the following datasets as `tibbles`/`data.frames`:

```{r}
library(badata)

employees_by_workplace

employees_by_residence

unemployed_total

unemployed_foreigners

jobs
```

Codes and full names of regions and occupational groups can be looked up in the respective tables:

```{r}
region_codes

occupational_group_codes
```

## Citation

```{r echo=FALSE, results='asis'}
print(citation("badata"), bibtex = FALSE)
```

A BibTeX entry for LaTeX users is

```{r echo=FALSE, comment=""}
toBibtex(citation("badata"))
```

## Disclaimer

The variable names were translated from German into English, the data itself remains unchanged and is subject to the copyright of the German Federal Employment Agency (BA). © [Statistik der Bundesagentur für Arbeit](https://statistik.arbeitsagentur.de)

This package is in no way officially related to or endorsed by BA.
